AbxD01 Analysis

### 2014-11-20 abxD01_analysis.Rmd
updated figure 3 files

### TO DO STILL
- I want to change the graph so that the OTUs are their own graphs and the titrations are side by side
- once code is working then put up the other titration data files
- change min relabund from 0.0001 to 0.001 for cef and strep
    - **11/20/14, changed the vanc titrations min**

>>>>

### TO DO STILL
- I want to change the graph so that the OTUs are their own graphs and the titrations are side by side
    -**11/20/14, completed most of the graphical parameters.*
- once code is working then put up the other titration data files
- change min relabund from 0.0001 to 0.001 for cef and strep
    - **11/20/14, changed the vanc titrations min**
- *Possibly work on merging singles*
- *Possibly work on getting plots on top of grid lines*
